Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{multirow}
\usepackage{tabularx, colortbl, makecell}

@@

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{cccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{DNSMOS} & \multirow{2}{*}{dWER} & \multirow{2}{*}{Spk Sim} \\
                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\
            \hline
            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-wavlm   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-wavlm        & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
      \end{center}
      \caption{This table }
  \end{table*}

@@

\subsection{Baseline models}

TSELM is compared with

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{multirow}
\usepackage{tabularx, colortbl, makecell}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\@makecaption}
  {\scshape}
  {}
  {}
  {}
\makeatother

@@

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{cccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{DNSMOS} & \multirow{2}{*}{dWER} & \multirow{2}{*}{Spk Sim} \\
                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\
            \hline
            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{Sample table showing different categories of items with their quantities.}
            \label{main_exp}
            This table 
      \end{center}

  \end{table*}

@@

\subsection{Baseline models}
All models are reflected in Table \ref{main_exp}. 
TSELM is compared with Spex+, a discriminative separation model \cite{spex_plus} trained on Libri2Mix \cite{librimix}. Since the discretization might lose some 
speaker information compared with continuous methods. We compare the speaker 
similarity of TSELM with the target audio produced by discretizating the clean audio, which is denoted by Target-discrete-WavLM.
